---
title: "Network of Thrones Recreation in R"
author: "Aaron Trask"
date: "6/23/2016"
output: html_document
description: "Drawn from Network of Thrones by Andrew Beveridge and Jie Shan which was published in the April 2016 Math Horizons www.maa.org/mathhorizons"

```{r setup, include=FALSE}
require(igraph)
require(scales)
require(ggplot2)
require(grid)
require(dplyr)
```

## Loading the Network

The authors published their graph as a list of edges with weights in csv format.  Here we load it into a table and then create the graph object from the table.

```{r}
t <- read.csv("stormofswords.csv", header=TRUE)
g <- graph.data.frame(t,directed=FALSE)
```

## Exploring the Network
### Page Rank
```{r}
V(g)$page_rank <- page_rank(g)$vector
pr <- data.frame(name = V(g)$name, page_rank = V(g)$page_rank)
ggplot(pr, aes(x = reorder(name, -page_rank), y = page_rank)) + 
  geom_bar(data = subset(pr, page_rank > quantile(page_rank, prob = 0.90)), stat = "identity") + 
  theme(axis.text.x = element_text(angle=90))
```

### Betweenness
```{r}
V(g)$betweenness <- betweenness(g)
bc <- data.frame(name = V(g)$name, betweenness = V(g)$betweenness)
ggplot(bc, aes(x = reorder(name, -betweenness), y = betweenness)) + 
  geom_bar(data = subset(bc, betweenness > quantile(betweenness, prob = 0.90)), stat = "identity") + 
  theme(axis.text.x = element_text(angle=90))
```

### Compute Clusters
```{r}
communities <- cluster_louvain(g)
```

## Plotting the Network

```{r}
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
V(g)$label <- V(g)$name
V(g)$label.cex <- rescale(V(g)$betweenness, c(0.5,1.5)) #size the label by the betweenness
V(g)$label.family <- "Century Gothic"
V(g)$label.font <- 2
V(g)$label.degree <- pi/2
V(g)$label.dist <- V(g)$label.cex/4
V(g)$size <- rescale(V(g)$page_rank, c(1,5)) #size the verticies by their page rank
V(g)$frame.color <- "white"
V(g)$color <- cbPalette[membership(communities)] #color the verticies by the cluster membership
E(g)$arrow.mode <- 0
E(g)$width <- rescale(E(g)$Weight, c(1,5)) #weight the edges
E(g)$curved <- .5
plot(g, layout=layout.davidson.harel)
```